\cvsection{Experience}

\begin{cventries}
  \cventry
    {Application Programmer Analyst} % Job title
    {BBVA} % Organization
    {Birmingham, AL} % Location
    {Oct. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Work directly with Lines of business to build and maintain internal banking web applications }
        \item {Perform regular maintenance on AWS Cloud based servers including setting up IIS, ASP.Net Environments, Linux Servers (Redhat) and SQL Server Maintenance}
        \item {Work in an agile environment with multiple team members to provide support, peer reviews and feed back to help cut down on roadblocks and productivity decreases}
        \item {Provide technical support for vendor applications including maintenance, installation and upgrades}
      \end{cvitems}
    }

  \cventry
    {Programmer (Contract to hire)} % Job title
    {ITAC Solutions} % Organization
    {Birmingham, AL} % Location
    {Apr. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Updated the look and feel of 15 web applications for BBVA's new branding changes, modernized 10-15+ year old applications to modern security and programming standards, provided support for FT employees on my team.}
        \item {Helped migrate web applications to Bitbucket/Bamboo to modernize team workflow and ease collaboration on bigger projects.}
      \end{cvitems}
    }

  \cventry
    {Programmer} % Job title
    {Pentius} % Organization
    {Remote} % Location
    {Apr. 2015 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped lead a team of developers to modernize the web based callcenter customer service dashboard from classic asp web pages to a single page javascript web app that performed asynchronously and decreased server load for page loads. This included building and maintaing an API that could be used across different callcenter functionality ranging from VOIP telephone calls to real-time KPI reports.}
        \item {Created a real-time diagnostic tool that was capable of getting technical statistics of any ongoing or past calls. This report, originally created for techincal teams, was morphed and eventually used by managers to track employees productivity and administration.}
        \item {Worked with a team of developers to implement a interactive voice response (IVR) system to direct customers to callcenter agents according to responses provided via keypad input}
        \item {Built and maintained reports with multiple search options and drilldowns, modernized reports by adding bootstrap and/or google mdl theme for better readability and maintenance}
      \end{cvitems}
    }

\end{cventries}
